---
title: "Creating a metadata.JSON"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a metadata.JSON}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  options(rmarkdown.html_vignette.check_title = FALSE)
)
```

```{r setup}
library(GradingAccuracy)
```

# Requirements for metadata.json

A `metadata.json` file can be used to keep track of information on the course-, assignment- and question-level. While additional arguments may be added to keep track of other miscellaneous information, this package requires that the `metadata.json` has a `course_info` object and a `rubric object`.

The `course_info` object must have the following keys (and their corresponding values):

- `department` : department abbreviation (e.g. "STAT", "DATA")
- `course_number` : course number
- `course_name` : name of course (e.g. "Introduction to Probability")
- `upper_div` : if the course is upper-division or lower-division
-  `year` : year of the course
- `semester` : semester of the course (e.g. "Spring", "Fall")
- `assignment_name` : name of assignment (e.g. "Midterm 1")
- `question_number` : number of question, including subparts (e.g. "5c")
- `question_name` : name of question (e.g. "Data Visualization")
- `mode_of_question` : mode of question (e.g. "fill in the blank", "open-ended")
- `medium_of_answer` : medium of student's answer (e.g. "handwritten", "typed")
- `content_of_answer` : expected content of student's answer (e.g. "English", "math", "code")
- `scoring_type` : whether the scoring is positive (i.e. additive) or negative (i.e. subtractive)
- `is_proctored` : whether the assignment was taken in a proctored environment or if it was take-home
- `n_submissions`: the number of student submissions, which can be programmatically updated with `update_scores_in_metadata()`
- `mean_score`: the mean score of experts using, which can be programmatically updated with `update_scores_in_metadata()` (which uses `mean(experts$Score/max(experts$Score))`)
- `total_points`: the total number of points the question is worth
- `rubric_type`: the type of rubric (e.g. `"positive disjoint"`)


The `rubric` object must have a `calibrated` rubric object and optionally an `uncalibrated` object that follows the same structure. A rubric object (either `calibrated` or `uncalibrated`) must have the following structure:

  - `rubric_items` which is a nested list that has keys named as "R1", "R2", etc. with values as strings of the rubric description
  - `scores`, which is a numbered vector that has the corresponding point value of rubric items "R1", "R2",...

## Correct Metadata.json with only a `calibrated` rubric

``` yaml
`r xfun::file_string(system.file("extdata", "metadata-calibrated.json", package = "GradingAccuracy"))`
```

## Correct Metadata.json with a `calibrated` and `uncalibrated `rubric

``` yaml
`r xfun::file_string(system.file("extdata", "metadata-uncalibrated.json", package = "GradingAccuracy"))`
```

# Validating a metadata.json

The `validate_metadata_json()` function can be used to validate that all required arguments and keys are present and correctly formatted.

## Correct metadata.json file

If you have a correct `metadata.json` file, like the example file above, you will receive the following message:

```{r}
validate_metadata_json(system.file("extdata", "metadata-calibrated.json", package = "GradingAccuracy"))
```

Optionally, you can also use the `verbose` argument in order to print out the listed course and assignment information stored in this JSON file:

```{r}
validate_metadata_json(system.file("extdata", "metadata-calibrated.json", package = "GradingAccuracy"), verbose = T)
```

## `course_info`: Potential Errors

### Missing `course_info`

For example, if you are missing the `course_info` argument, like in the JSON file below:

``` yaml
`r xfun::file_string(system.file("extdata", "missing-course-info.json", package = "GradingAccuracy"))`
```

you will get the following error:

```{r, echo = F}
# this should give an error
testthat::expect_error(validate_metadata_json(system.file("extdata", "missing-course-info.json", package = "GradingAccuracy")))
```


```{r, error = T}
validate_metadata_json(system.file("extdata", "missing-course-info.json", package = "GradingAccuracy"))
```

### Missing Required Keys

If you are missing the required keys, like in the JSON file below:

``` yaml
`r xfun::file_string(system.file("extdata", "missing-keys.json", package = "GradingAccuracy"))`
```

you will get the following error:

```{r, echo = F}
# this should give an error
testthat::expect_error(validate_metadata_json(system.file("extdata", "missing-keys.json", package = "GradingAccuracy")))
```


```{r, error = T}
validate_metadata_json(system.file("extdata", "missing-keys.json", package = "GradingAccuracy"))
```

### Incorrect Data Types

If the required keys have an incorrect data type, like if `upper-div` is not a boolean value as in the example below:

``` yaml
`r xfun::file_string(system.file("extdata", "wrong-boolean.json", package = "GradingAccuracy"))`
```

you will get the following error:

```{r, echo = F}
# this should give an error
testthat::expect_error(validate_metadata_json(system.file("extdata", "wrong-boolean.json", package = "GradingAccuracy")))
```


```{r, error = T}
validate_metadata_json(system.file("extdata", "wrong-boolean.json", package = "GradingAccuracy"))
```

## `rubric`: Potential Errors

Note that if the `uncalibrated` rubric item is not empty, these checks are applied to both `uncalibrated` and `calibrated`, but the checks are only applied to the latter if `uncalibrated` is empty.

### Mismatched Rubric Items and Scores

For example, if the number of `rubric_items` and the number of `scores` are not equal, like in the JSON file below:

``` yaml
`r xfun::file_string(system.file("extdata", "mismatched-rubric-scores.json", package = "GradingAccuracy"))`
```

you will get the following error:

```{r, echo = F}
# this should give an error
testthat::expect_error(validate_metadata_json(system.file("extdata", "mismatched-rubric-scores.json", package = "GradingAccuracy")))
```


```{r, error = T}
validate_metadata_json(system.file("extdata", "mismatched-rubric-scores.json", package = "GradingAccuracy"))
```

### Scores Are Not Numbers

If the `scores` are not numbers, like in the JSON file below:

``` yaml
`r xfun::file_string(system.file("extdata", "incorrect-scores.json", package = "GradingAccuracy"))`
```

you will get the following error:

```{r, echo = F}
# this should give an error
testthat::expect_error(validate_metadata_json(system.file("extdata", "incorrect-scores.json", package = "GradingAccuracy")))
```


```{r, error = T}
validate_metadata_json(system.file("extdata", "incorrect-scores.json", package = "GradingAccuracy"))
```

### Incorrectly Named Keys

If you do not name the keys in `rubric items` according to expected structure (e.g. "R1", "R2", ...), like in the JSON file below:

``` yaml
`r xfun::file_string(system.file("extdata", "incorrect-rubric-keys.json", package = "GradingAccuracy"))`
```

you will get the following error:

```{r, echo = F}
# this should give an error
testthat::expect_error(validate_metadata_json(system.file("extdata", "incorrect-rubric-keys.json", package = "GradingAccuracy")))
```


```{r, error = T}
validate_metadata_json(system.file("extdata", "incorrect-rubric-keys.json", package = "GradingAccuracy"))
```
